On The Impact of Atoms of Confusion in JavaScript Code

### 2021-04-25 3_Method.tex
reduced the size of the tables

\begin{table*}[htb!]
\centering
\begin{tabular}
{p{0.4cm}p{0.9cm}p{2.0cm}p{6cm}p{1.9cm} p{4.5cm}}
\toprule
ID & Gender & Level & Role & JS Experience & Other Languages \\ \midrule 
P1 & Male & Graduate & Software Developer & 9 years & Java, PHP, C, Go  
\\ 
P2 & Male & High School & Software Developer & 3 years & Python, Go, Dart, Lua, C++, C\#
\\ 
P3 & Male & Graduate & Software Developer & 4 years & Java, C
\\ 
P4 & Male & Undergraduate & Software Developer & 3 years & Python, C, C++, Java, Go
\\ 
P5 & Male & Master Student & Software Developer & 3 years & Python, SQL
\\ 
P6 & Male & Graduate & Software Architect  & 15  years  & Java, PHP, C, Python , Ruby, C\# and R
\\ 
P7 & Male & Graduate & Software Developer  & 6 years & C, C++, Java, Assembly, Kotlin
\\ 
P8 & Male & PhD & Software Developer & 2 years & Java, Python
\\ 
P9 & Male & Graduate & Business Analyst and Software Developer & 5 years & PHP
\\ 
P10 & Male & Master Student & Business Analyst and Software Developer  & 4 years & Java, C\# and Python
\\ 
P11 & Male & Master Student & Software Architect & 4 years & Java, Erlang, C\#, Cobol
\\ 
P12 & Female & Master & Software Developer  & 1 year & C
\\ 
P13 & Male & Master & Software Developer & 13 years & Java, PHP
\\ 
P14 & Female & Master Student & Software Developer  & 3 years & C, Python, Ruby
\\ 
P15 & Female &  Graduate & Software Developer & 2 years & Java, PHP
\\ \bottomrule
\end{tabular}
    \caption{Demographic information of the participants}
    \label{pinterview}
\end{table*}

@@

\begin{table*}[ht]
 \centering
 \begin{tabular}{rrrrrrr}
   \hline
             & Min. & 1st Qu. & Median & Mean & 3rd Qu. & Max. \\ \hline
 Lines of Code           & \num{5543}  & \num{16060.25} & \num{36161.5} & \num{111432.33} & \num{111182.50} & \num{1278405} \\
 Num. of Forks     & \num{1244}   & \num{3029.75} & \num{6078} & \num{8906.24} & \num{9260.50} & \num{68849} \\
 Num. of Contributors  & \num{6}   & \num{184} & \num{285.5} & \num{533.44} & \num{515.75} & \num{4047} \\
 Num. of Stars        & \num{23672} & \num{27055} & \num{34990} & \num{46919.51} & \num{48518} & \num{310935} \\

    \hline
 \end{tabular}
 \caption{Some descriptive statistics about the projects used in the MSR study}
 \label{tab:projects-statistics} 
 \end{table*}

>>>>

\begin{table}[htb!]
  \centering
\begin{scriptsize}  
\begin{tabular}{clcl}
\toprule
ID & Education & JS Experience & Other Languages \\ \midrule 
P1 & BSc Degree & 9 years & Java, PHP, C, Go  
\\ 
P2 & HS Degree & 3 years & Python, Go, Dart, Lua, C++, C\#
\\ 
P3 & BSc Degree & 4 years & Java, C
\\ 
P4 & Undergraduate & 3 years & Python, C, C++, Java, Go
\\ 
P5 & Master Student & 3 years & Python, SQL
\\ 
P6 & Bsc Degree & 15  years  & Java, PHP, C, Python , Ruby, C\# and R
\\ 
P7 & BSc Degree  & 6 years & C, C++, Java, Assembly, Kotlin
\\ 
P8 & PhD Degree & 2 years & Java, Python
\\ 
P9 & BSc Degree  & 5 years & PHP
\\ 
P10 & Master Student & 4 years & Java, C\# and Python
\\ 
P11 & Master Student & 4 years & Java, Erlang, C\#, Cobol
\\ 
P12 & Master Degree & 1 year & C
\\ 
P13 & Master Degree & 13 years & Java, PHP
\\ 
P14 & Master Student & 3 years & C, Python, Ruby
\\ 
P15 &  BSc degree  & 2 years & Java, PHP
\\ \bottomrule
\end{tabular}
\end{scriptsize}
    \caption{Demographic information of the participants}
    \label{pinterview}
\end{table}

@@

\begin{table}[ht]
  \centering
  \begin{scriptsize}
 \begin{tabular}{rrrrr}
   \hline
                       & Min.             & Median        & Mean             & Max. \\ \hline
 Lines of Code         & \num{5543}       & \num{36161.5} & \num{111432.33}  & \num{1278405} \\
 Num. of Forks         & \num{1244}       & \num{6078}    & \num{8906.24}    & \num{68849} \\
 Num. of Contributors  & \num{6}          & \num{285.5}   & \num{533.44}     & \num{4047} \\
 Num. of Stars         & \num{23672}      & \num{34990}   & \num{46919.51}   & \num{310935} \\

    \hline
 \end{tabular}
 \end{scriptsize}
 \caption{Some descriptive statistics about the projects used in the MSR study}
 \label{tab:projects-statistics} 
 \end{table}
